Refinements for open pNets

### 2021-07-19 2021-Refinement/paper/refinementarticle.tex
open automata def

@@

>>>>

\begin{definition}[Open automaton]
An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
A pair of a state and a valuation is called a configuration.
\end{definition}
We suppose that each automaton has a distinct set of variables. If there is a clash of variable names we suppose that there is still a way to  distinguish them.

%%% LUDO STOPPED HERE

\begin{definition}[Open transition, Instanciated transition]
An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
An open transition can have many unbound variables.

An instanciated transition of the automaton is transition produced by any well-formed substitution of the unbound variables of the transition minus the automaton variables.
\end{definition}
The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
The LTS is partial in the sense that one can plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
In any configuration, it can perform instanciated transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
An instanciated transition is a transition where every variable that is not an automaton variable is instantiated with a value.
By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.

@@

\section{a recuperer si on se rend comtpte que c'est utile}
When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
